### 2017-08-12 Docs/Thesis/docs/chapter4.tex
some modifications on the thesis
3rd revision of the thesis text complete, apA and apB completed. Still have to finish apC and apD

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Modeling and Algorithms}\label{ch:modeling-evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%2nd-review
In this chapter, we propose a method that may be implemented by  software. We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}. Since generating random can be cost and have a bias, depending on the seed generator, we cut these problems since our method is analytical.

%2nd-review
We made a brief bibliographic review of some works related works on this topic. Then, we will present the traffic traces we are going to use in this chapter, and in the rest of our work. After we present or selected method for parameterization and fitting choice. To test our criteria quality, we define a validation method, based on cross-validations made by simulations.

@@

%2nd-review
The third we capture in our laboratory LAN, through a period of 24 hours. It was captured in the firewall gateway between our local and external network. Along with other tests, We intend to verify diurnal behavior on it. That means a high demand of packets during the day and a small in the night. We call it \textit{lan-diurnal-pcap}.

%2nd-review
The fourth is a capture of a busy private network access point to the Internet, available on-line on TCPreplay\cite{web-tcpreplay} website \footnote{ http://tcpreplay.appneta.com/wiki/captures.html}, and is called \texttt{bigFlows.pcap}. We will refer to it \textit{bigflows-pcap}.

@@

%2nd-review
We summarize our process of modeling inter-packet times at the figure~\ref{fig:model-parameterization}. We collect a set of inter-packet times from an actual traffic capture. Then, we estimate a set of parameters for stochastic functions, using different methodologies. Then, from these parametrized models, we estimate which best represent our data set, using the measure of quality AIC (Akaike information criterion). We also calculate another measure of quality called BIC(Bayesian information criterion), for comparison of results. In this chapter, we present our results obtained on our prototype implemented in Octave.

@@

%2nd-review
Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood. We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:revision-probability}.

%2nd-review
Some observations must be made. Since the time samples resolution used were of $10^{-6}$s, all values equal to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero. To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively.

%2nd-review
We implemented this prototype using Octave. We upload the code on GitHub, for reproduction purposes\footnote{github-link-aqui}

@@

Manipuling the equation:
\begin{equation}
\alpha\ln{(t)} - \alpha\ln{(\beta)} = \ln{-\ln{1 - F(t)}}
\end{equation}

%%2nd-review
If we call $x = \ln{(t)}$ and $y = \ln{(-\ln{(1 - F(t))})}$, we found a linear equation, where $a = \alpha$ and $b = -\alpha\ln{(\beta)}$. Having in hands a estimation of the empirical CDF of our data samples, we apply the $x$ and $y$ definitions to linearize the data. Using the gradient descendant, we are able to find a estimation of the linear coefficients $\hat{a}$ and $\hat{b}$. Using the inverse function of the definition of linear coefficients, we are able to find the estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.

@@

%2nd-review
We present examples of linearized data, and the linear approximation achieved, as well the cost convergence of the gradient descendant algorithm in the appendix ~\ref{ap:revision-probability}.

%2nd-review
Applying the inverse equations of the linear coefficients ($\hat{\alpha} = \hat{a}$ and $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$) (the symbol stands for the estimated parameters). So we are able to estimate the Weibull distribution parameters.

%2nd-review
We can summarize this procedure, in these steps:
\begin{enumerate}
\item Linearize the stochastic CDF function F(t).
\item Apply the linearized $y = y(F(t))$ and  $x = x(t)$ on the empirical CDF and times datasets, respectively. 
\item Use Gradient Descendant algorithm to find linear coefficients $a$ and $b$.
\item Apply the inverse equation of the linear coefficients, to determine the stochastic function parameters.
\end{enumerate}

%2nd-review
In the parameters estimation, there is an exception, since the Pareto scale ($t_{m}$) is defined by the minimum time.

%2nd-review
In the table~\ref{tab:linearization-sumary} we present a summary of the used equations in the procedure. In this notation, the subscript $i$ means that it must be applied on every empirical value measured. The hat( $\widehat{}$ ) indicates an estimated value for a parameter.

%2nd-review
In the figure~\ref{fig:linearization} we presente the linearized

%2nd-review
\begin{table}[h!]
	\centering
	\caption{Linearized functions, and parameters estimators, used by the linear regression}
	\label{tab:linearization-sumary}
	\begin{tabular}{llllll}
		\hline
		Function    & Linearized $x$     & Linearized $y$                    & \multicolumn{2}{l}{Parameters Estimator}      						 &  \\
		\hline
		Cauchy      & $x_i = t_i$        & $y_i = \tan{(\pi(F(t_i) - 1/2))}$ & $\hat{\gamma} = \frac{1}{\hat{a}}$ & $\hat{t_0} = - \frac{\hat{b}}{\hat{a}}$                      &  \\
		Exponential & $x_i = t_i$        & $y_i = \ln{(1 - F(t_i))})$        & \multicolumn{2}{l}{$\hat{\lambda} = -\hat{a}$}                                              &  \\
		Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 = F(t_i))}$         & $\hat{\alpha} = -\hat{a} $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
		Weibull     & $x = \ln{(t)}$     & $y = \ln{(-\ln{(1 - F(t))})}$     & $\hat{\alpha} = \hat{a}$                 & $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$                                   & \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[ht!]
\centering
\subfloat[c]{
  \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Linearized_data_and_linear_fitting}
  \label{fig:linearization}
}
%\hspace{0mm}
\subfloat[c]{
  \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Cost_J_iterations__convergence}
  \label{fig:cost}
}
\label{fig:linearization-cost}
\end{figure}

@@

%2nd-review
For the exponential distribution $E(X) = \frac{1}{\lambda}$, therefore:
\begin{equation}
\hat{\lambda} = \frac{1}{\hat{\mu}}
\end{equation}

@@

\subsubsection{AIC and BIC}

%2nd-review
 Suppose that we have an statistical model $M$ of soma dataset ${\boldsymbol{x} = (x_1, ..., x_n)}$, with $n$ independent and identically distributed observations of a random variable $X$. This model can be expressed by a PDF $f(x, \boldsymbol{\theta})$, where $\boldsymbol{\theta}$ a vector of parameter of the PDF, $\boldsymbol{\theta} \in \mathbb{R}^{k}$ ($k$ is the number of parameters). The  likelihood function  of this model $M$ is given by:

\begin{equation}
L(\boldsymbol{\theta}|\boldsymbol{x} ) =  f(x_1|\boldsymbol{\theta})...f(x_n|\boldsymbol{\theta}) = \prod_{i = 1}^{n}f(x_i|\boldsymbol{\theta})
\end{equation}

Now, suppose we are trying to estimate the best statistical model, from a set ${M_1, ..., M_n}$, each one whit an estimated vector of parameters  ${\boldsymbol{\hat{\theta_1}}}, ..., {\boldsymbol{\hat{\theta_n}}}$. $AIC$ and $BIC$ are defined by:

\begin{equation}
AIC = 2k - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}

\begin{equation}
BIC = k\ln(n) - \ln(L(\boldsymbol{\hat{\theta}}|\boldsymbol{x}))
\end{equation}

In both cases, the preferred model $M_i$, is the one with the smaller value of $AIC_i$ or $BIC_i$.

@@

%2nd-review
\begin{itemize}
\item Correlation between the sample data and the estimated model;
\item Hurst exponent;
\item Mean inter packet time;
\item Standard deviation of inter packet times.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%
% Prototype results
\begin{table}[h!]
	\centering
	\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}. \textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}
	\label{tab:prototype-results}
	\scalebox{0.75}{ 
		\begin{tabular}{lcccccccc}
			\hline
			& \multicolumn{8}{c}{Trace} \\ \cline{2-9} 
			Function		& AIC  & BIC  & \multicolumn{2}{c}{Parameters}  
			& AIC & BIC  & \multicolumn{2}{c}{Parameters} \\ \hline

			& \multicolumn{4}{c}{skype-pcap}  & \multicolumn{4}{c}{lan-diurnal-pcap}   \\ \hline 
			Cauchy          & $2.18e4$    & $2.19e4$    & $\gamma:2.59e-4$ & $x_0:1.05e-1$    
			& $-2.85e7$   & $-2.85e7$   & $\gamma:9.63e-3$ & $x_0:-3.61e-3$    \\
			Exponential(LR) & $-1.61e3$   & $-1.60e3$   & \multicolumn{2}{c}{$\lambda:1.86$}   
			& $1.79e6$    & $1.79e6$    & \multicolumn{2}{c}{$\lambda:8.51e-1$}    \\
			Exponential(Me) & $-4.29e3$   & $-4.28e3$   & \multicolumn{2}{c}{$\lambda:7.01$}   
			& $-3.12e7$   & $-3.12e7$   & \multicolumn{2}{c}{$ \lambda:58.78$} \\
			Normal          & $3.29e3$    & $3.31e3$    & $\mu:1.43e-1 $    & $\sigma:5.01e-1$ 
			& $Inf$       & $Inf$       & $\mu:1.70e-2$     & $\sigma:8.56e-2$ \\
			Pareto(LR)      & $-8.28e3$   & $-8.27e3$   & $\alpha:2.52e-1$ & $x_m:5e-8$    
			& $-4.60e7$   & $-4.60e7$   & $\alpha:2.55e-1$ & $ x_m:5e-8$    \\
			Pareto(MLH)     & $-1.16e4$   & $-1.16e4$   & $\alpha:9.21e-2$ & $x_m:5e-8$    
			& $-5.03e7$   & $-5.03e7$   & $\alpha:1.15e-1$ & $ x_m:5e-8$    \\
			Weibull         & $-1.46e4$   & $ -1.46e4$  & $\alpha:3.20e-1$ & $\beta:1.52e-2$  
			& $-5.60e7$   & $-5.60e7$   & $\alpha:3.34e-1$ & $\beta:1.83e-3$  \\ \hline	
			& \multicolumn{4}{c}{bigFlows-pcap} & \multicolumn{4}{c}{wan-pcap}  \\ \hline
			Cauchy          & $7.14e6$    & $7.14e6$   & $\gamma:1.94e0$ &$x_0:-7.25$    
			& $5.99e7$    & $5.99e7$   & $ \gamma:8.28e2$ &$x_0:-4.52e3$    \\
			Exponential(LR) & $7.33e6$    & $7.33e6$   & \multicolumn{2}{c}{$\lambda:1.489e-1$}   
			& $5.68e7$    & $ 5.68e7$  & \multicolumn{2}{c}{$\lambda:2.2e-5$}   \\
			Exponential(Me) & $-1.09e7$   & $-1.09e7$  & \multicolumn{2}{c}{$\lambda:2.64e3$}   
			& $-6.58e7$   & $-6.58e7$  & \multicolumn{2}{c}{$\lambda:6.58e5$} \\
			Normal          & $-9.35e6$   & $-9.35e6$  & $\mu:3.79e-4$   &$\sigma:6.60e-4$ 
			& $-6.39e7$   & $-6.39e7$  & $\mu:2e-6$     & $\sigma:1e-6$ \\
			Pareto(LR)      & $-1.02e7$   & $-1.02e7$  & $\alpha:1.489e-1 $ & $x_m:5e-8 $    
			& $-5.31e7$   & $-5.31e7$  & $\alpha:NaN$ & $x_m:5e-8 $    \\
			Pareto(MLH)     & $-1.03e7$   & $-1.03e7$  & $\alpha:1.362e-1$ & $x_m:5e-8 $    
			& $-6.25e7$   & $-6.25e7$  & $\alpha:3.39e-1$ & $x_m:5e-8 $    \\
			Weibull         & $-1.10e7$   & $-1.10e7$  & $\alpha:2.81e-1$ & $\beta:5.54e-4$  
			& $-5.46e7$   & $-5.46e7$  & $\alpha:7.64e-2$ & $\beta:1e-6$  \\ \hline
		\end{tabular}
	}
\end{table}

@@

The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results1}.  The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results}. The difference between BIC and AIC values in all simulations are very small. Much smaller then the difference between its values between the distributions. This is an indication that for inter packet times, using AIC or BIC should will not influence significantly the results.

On our previsions, Weibull and Pareto(MLH and LR) are the best options. This was expected, since both are heavy-tailed functions. But, Cauchy, on most of the tests, even being a heavy-tailed distribution seems to no present a good fitting. This is effect of the fast divergence of tangent function, when we linearize our data.

@@

All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BI and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.

@@

%%%%%%%%%%%%%%
% Skype correlation, Hurst, Mean Standard Deviation
\begin{figure}[h!]
	\centering
	\subfloat[Correlation]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Correlation}
		\label{correlation-skype}
	}
	\hspace{0mm}
	\subfloat[Hust Exponent]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Hurst_Exponent}
		\label{hurst-skype}
	}
	\hspace{0mm}
	\subfloat[Mean]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Mean}
		\label{mean-skype}
	}
	\hspace{0mm}
	\subfloat[Standard Deviation]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Standard_Deviation}
		\label{std-skype}
	}
	\caption{Statistical parameters of \textit{skype-pcap} and its approximations}
	\label{fig:correlation-hurst-skype-pcap}
\end{figure}

%validation Cost function
\begin{figure}[ht!]
	\centering
	\subfloat[\textit{skype-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/Skype_costFunction}
		\label{cost-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{bigFlows-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/bigFlows_costFunction}
		\label{cost-bigFlows-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{lan-diurnal-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/Lan_costFunction}
		\label{cost-lan-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{wan-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/Wan_costFunction}
		\label{cost-wan-pcap}
	}
	\caption{Cost function for each one of the datasets used in this validation process}
	\label{fig:cost-function}
\end{figure}

@@

Also, except by the Pareto function modeled using the Maximum likelyhood method, have comparative results between the simulations and the AIC/BIC gess. The best fittings according to the AIC/BIC usually  returned very acurate models, with close mean and fractal level, and correlation close to one. The models selected as the worsts usually returned poor results.

Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurante fitting, what justify the application of the criteria in all new experiment.

We do not rely on only one type of parametrization. This turns our methodology more robust, since a linear regression may diverge. But aways there will be an packable model, since our estimations for Normal, Exponential(Me) and Pareto(MLH) cannot. Models wich the linear regression diverge, will not have god BIC/AIC estimations, and will not be pickedas primary options.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Traffic Modeling and Algorithms}\label{ch:modeling-evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%2nd-review
In this chapter, we propose a method automatizable by  software. We estimate many stochastic functions through many methodologies and select the best model through the AIC computation\cite{bic-aic-comparision}. Since generating random can be cost and have a bias, depending on the seed generator, we avoid these problems since our method is analytical.

%2nd-review
We made a brief bibliographic review of some related works on this topic. Then, we will present the traffic traces we are going to use in this chapter, and in the rest of our work. After we present or selected method for parameterization and fitting choice. To test our criteria quality, we define a validation method, based on cross-validations made by simulations.

@@

%2nd-review
The third we capture in our laboratory LAN, through a period of 24 hours. It was captured irewall gateway between our local and external network. Along with other tests, We intend to verify diurnal behavior on it. That means a high demand of packets during the day and a small in the night. We call it \textit{lan-diurnal-pcap}.

%2nd-review
The fourth is a capture of a busy private network access point to the Internet, available on-line on TCPreplay website \footnote{ \href{http://tcpreplay.appneta.com/wiki/captures.html}{http://tcpreplay.appneta.com/wiki/captures.html}}, and is called \texttt{bigFlows.pcap}. We will refer to it \textit{bigflows-pcap}.

@@

%2nd-review
We summarize our process of modeling inter-packet times at the figure~\ref{fig:model-parameterization}. We collect a set of inter-packet times from an actual traffic capture. Then, we estimate a set of parameters for stochastic functions, using different methodologies. Then, from these parametrized models, we estimate which best represent our data set, using the measure of quality AIC (Akaike information criterion). We also calculate another measure of quality called BIC(Bayesian information criterion), for comparison of results. In this chapter, we present our results obtained on our prototype implemented in Octave\footnote{ \href{https://www.gnu.org/software/octave/}{https://www.gnu.org/software/octave/}}.

@@

%2nd-review
Now we will give a brief explanation our three procedures: Linear Regression (with the  Gradient descendant algorithm), direct estimation, and maximum likelihood. Some observations must be made. Since the time samples resolution used were of $10^{-6}$s, all values equal to zero were set to  $5\cdot10^{-8}$s, to avoid division by zero. To avoid divergence on tangent operation on the linearization the Cauchy function, the inter-packets CDF function values were floor-limited and upper-limited to  $10^{-6}$ and $0.999999$ respectively. We implemented this prototype using Octave. We upload the code on GitHub, for reproduction purposes\footnote{\textcolor{red}{github-link-aqui}}

%We go deep into details explaining the methods on the appendix ~\ref{ap:revision-probability}, and present the mathematical demonstrations on appendix~\ref{ap:revision-probability}.

@@

Manipuling the equation:
\begin{equation}
\alpha\ln{(t)} - \alpha\ln{(\beta)} = \ln{(-\ln{(1 - F(t))})}
\end{equation}

%%2nd-review
If we call $x = \ln{(t)}$ and $y = \ln{(-\ln{(1 - F(t))})}$, we found a linear equation, where $a = \alpha$ and $b = -\alpha\ln{(\beta)}$. Having in hands a estimation of the empirical CDF of our data samples, we apply the $x$ and $y$ definitions to linearize the data.

Using the gradient descendant, we find a estimation of the linear coefficients $\hat{a}$ and $\hat{b}$. Using the inverse function of linear coefficients, we find the weibull estimated parameters $\hat{\alpha}$ and $\hat{\beta}$.

@@

The gradient descendent consists in minimizing a cost function $J(\theta)$. We explain this procedure in the appendix ~\ref{ap:revision-probability}. In the figure~\ref{fig:linearization} we present as examples, the linearized data for the inter arrivals from the \textit{skype-pcap}, and in the figure ~\ref{fig:linearization-cost} the cost convergence. In the appendix ~\ref{ap:aditional-plots}, a complete set of these figures is presented.

Applying the inverse equations of the linear coefficients ($\hat{\alpha} = \hat{a}$ and $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$) \footnote{The hat symbol ( $ \widehat{} $ ) for the estimated parameters}, we are able to estimate the Weibull distribution parameters. We can summarize this procedure, in these steps:
\begin{enumerate}
\item Linearize the stochastic CDF function F(t).
\item Apply the linearized $y = y(F(t))$ and  $x = x(t)$ on the empirical CDF and times datasets, respectively. 
\item Use Gradient Descendant algorithm to find linear coefficients $a$ and $b$.
\item Apply the inverse equation of the linear coefficients, to determine the stochastic function parameters.
\end{enumerate}

%2nd-review
In the parameters estimation (step 4), there is an exception, since the Pareto scale ($t_{m}$) is defined by the minimum time. In the table~\ref{tab:linearization-sumary} we present a summary of the used equations in the procedure. In this notation, the subscript $i$ means that it must be applied on every empirical value measured. The hat( $\widehat{}$ ) indicates an estimated value for a parameter.

%2nd-review
\begin{table}[h!]
	\centering
	\caption{Linearized functions, and parameters estimators, used by the linear regression}
	\label{tab:linearization-sumary}
	\begin{tabular}{llllll}
		\hline
		Function    & Linearized $x$     & Linearized $y$                    & \multicolumn{2}{l}{Parameters Estimator}      						 &  \\
		\hline
		Cauchy      & $x_i = t_i$        & $y_i = \tan{(\pi(F(t_i) - 1/2))}$ & $\hat{\gamma} = \frac{1}{\hat{a}}$ & $\hat{t_0} = - \frac{\hat{b}}{\hat{a}}$                      &  \\
		Exponential & $x_i = t_i$        & $y_i = \ln{(1 - F(t_i))})$        & \multicolumn{2}{l}{$\hat{\lambda} = -\hat{a}$}                                              &  \\
		Pareto      & $x_i = \ln{(t_i)}$ & $y_i = \ln{(1 - F(t_i))}$         & $\hat{\alpha} = -\hat{a} $         & $\hat{x_{m}} = \min_{i = 0, ..., m}\{x_{i}\}$ &  \\
		Weibull     & $x = \ln{(t)}$     & $y = \ln{(-\ln{(1 - F(t))})}$     & $\hat{\alpha} = \hat{a}$                 & $\hat{\beta} = e^{-(\hat{b}/\hat{a})}$                                   & \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[ht!]
\centering
\subfloat[Linearized interarrival data]{
  \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Linearized_data_and_linear_fitting}
  \label{fig:linearization}
}
%\hspace{0mm}
\subfloat[Cost function of the linear regression]{
  \includegraphics[height=50mm]{figures/ch4/Skype_Weibull_-_Cost_J_iterations__convergence}
  \label{fig:cost}
}
\label{fig:linearization-cost}
\caption{Linearized data and cost function of weibull linear regression}
\end{figure}

@@

%2nd-review
For the exponential distribution $E(X) = \frac{1}{\lambda}$, therefore we have:
\begin{equation}
\hat{\lambda} = \frac{1}{\hat{\mu}}
\end{equation}

@@

%\subsubsection{AIC and BIC}

@@

%2nd-review
\begin{itemize}
\item Correlation between the sample data and the estimated model (Pearson's product-moment coefficient);
\item Hurst exponent;
\item Mean inter packet time;
\item Standard deviation of inter packet times.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%
% Prototype results
\begin{table}[h!]
	\centering
	\caption{Results of the octave prototype, include BIC and AIC values, para estimated parameters for two of our pcap traces: \textit{skype-pcap }and \textit{bigflows-pcap}. \textit{bigflows-pcap} is much larger, and has a much much smaller mean inter-packet time}

	\scalebox{0.75}{ 
		\begin{tabular}{lcccccccc}
			\hline
			& \multicolumn{8}{c}{Trace} \\ \cline{2-9} 
			Function		& AIC  & BIC  & \multicolumn{2}{c}{Parameters}  
			& AIC & BIC  & \multicolumn{2}{c}{Parameters} \\ \hline

			& \multicolumn{4}{c}{skype-pcap}  & \multicolumn{4}{c}{lan-diurnal-pcap}   \\ \hline 
			Cauchy          & $2.18e4$    & $2.19e4$    & $\gamma:2.59e-4$ & $x_0:1.05e-1$    
			& $-2.85e7$   & $-2.85e7$   & $\gamma:9.63e-3$ & $x_0:-3.61e-3$    \\
			Exponential(LR) & $-1.61e3$   & $-1.60e3$   & \multicolumn{2}{c}{$\lambda:1.86$}   
			& $1.79e6$    & $1.79e6$    & \multicolumn{2}{c}{$\lambda:8.51e-1$}    \\
			Exponential(Me) & $-4.29e3$   & $-4.28e3$   & \multicolumn{2}{c}{$\lambda:7.01$}   
			& $-3.12e7$   & $-3.12e7$   & \multicolumn{2}{c}{$ \lambda:58.78$} \\
			Normal          & $3.29e3$    & $3.31e3$    & $\mu:1.43e-1 $    & $\sigma:5.01e-1$ 
			& $Inf$       & $Inf$       & $\mu:1.70e-2$     & $\sigma:8.56e-2$ \\
			Pareto(LR)      & $-8.28e3$   & $-8.27e3$   & $\alpha:2.52e-1$ & $x_m:5e-8$    
			& $-4.60e7$   & $-4.60e7$   & $\alpha:2.55e-1$ & $ x_m:5e-8$    \\
			Pareto(MLH)     & $-1.16e4$   & $-1.16e4$   & $\alpha:9.21e-2$ & $x_m:5e-8$    
			& $-5.03e7$   & $-5.03e7$   & $\alpha:1.15e-1$ & $ x_m:5e-8$    \\
			Weibull         & $-1.46e4$   & $ -1.46e4$  & $\alpha:3.20e-1$ & $\beta:1.52e-2$  
			& $-5.60e7$   & $-5.60e7$   & $\alpha:3.34e-1$ & $\beta:1.83e-3$  \\ \hline	
			& \multicolumn{4}{c}{bigFlows-pcap} & \multicolumn{4}{c}{wan-pcap}  \\ \hline
			Cauchy          & $7.14e6$    & $7.14e6$   & $\gamma:1.94e0$ &$x_0:-7.25$    
			& $5.99e7$    & $5.99e7$   & $ \gamma:8.28e2$ &$x_0:-4.52e3$    \\
			Exponential(LR) & $7.33e6$    & $7.33e6$   & \multicolumn{2}{c}{$\lambda:1.489e-1$}   
			& $5.68e7$    & $ 5.68e7$  & \multicolumn{2}{c}{$\lambda:2.2e-5$}   \\
			Exponential(Me) & $-1.09e7$   & $-1.09e7$  & \multicolumn{2}{c}{$\lambda:2.64e3$}   
			& $-6.58e7$   & $-6.58e7$  & \multicolumn{2}{c}{$\lambda:6.58e5$} \\
			Normal          & $-9.35e6$   & $-9.35e6$  & $\mu:3.79e-4$   &$\sigma:6.60e-4$ 
			& $-6.39e7$   & $-6.39e7$  & $\mu:2e-6$     & $\sigma:1e-6$ \\
			Pareto(LR)      & $-1.02e7$   & $-1.02e7$  & $\alpha:1.489e-1 $ & $x_m:5e-8 $    
			& $-5.31e7$   & $-5.31e7$  & $\alpha:NaN$ & $x_m:5e-8 $    \\
			Pareto(MLH)     & $-1.03e7$   & $-1.03e7$  & $\alpha:1.362e-1$ & $x_m:5e-8 $    
			& $-6.25e7$   & $-6.25e7$  & $\alpha:3.39e-1$ & $x_m:5e-8 $    \\
			Weibull         & $-1.10e7$   & $-1.10e7$  & $\alpha:2.81e-1$ & $\beta:5.54e-4$  
			& $-5.46e7$   & $-5.46e7$  & $\alpha:7.64e-2$ & $\beta:1e-6$  \\ \hline
		\end{tabular}
	\label{tab:prototype-results}
	}
\end{table}

@@

The results for the AIC, BIC and parameters of all four traces are at the table~\ref{tab:prototype-results}.  The results for \textit{wan-pcap} and \textit{lan-diurnal-pcap} are on the table ~\ref{tab:prototype-results}. The difference between BIC and AIC values in all simulations are very small. Much smaller then the difference of these values between the distributions. This is an indication that for inter packet times, using AIC or BIC should will not influence significantly the results.

On our previsions, Weibull and Pareto(MLH and LR) are the best options. This was expected, since both are heavy-tailed functions. But Cauchy on most of the tests, even being a heavy-tailed distribution, seems to no present a good fitting. This is effect of the fast divergence of tangent function, when we linearize our data.

@@

All these results are abstracted by the cost function $J$. As we can see, on all pcaps, the best function selected by BIC and AIC~\ref{tab:prototype-results} also had the small cost~\ref{fig:cost-function}.

@@

%%%%%%%%%%%%%%
% Skype correlation, Hurst, Mean Standard Deviation
\begin{figure}[t!]
	\centering
	\subfloat[Correlation]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Correlation}
		\label{correlation-skype}
	}
	\hspace{0mm}
	\subfloat[Hust Exponent]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Hurst_Exponent}
		\label{hurst-skype}
	}
	\hspace{0mm}
	\subfloat[Mean]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Mean}
		\label{mean-skype}
	}
	\hspace{0mm}
	\subfloat[Standard Deviation]{
		\includegraphics[width=75mm]{figures/ch4/Skype_Standard_Deviation}
		\label{std-skype}
	}
	\caption{Statistical parameters of \textit{skype-pcap} and its approximations}
	\label{fig:correlation-hurst-skype-pcap}
\end{figure}

%validation Cost function
\begin{figure}[t!]
	\centering
	\subfloat[\textit{skype-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/Skype_costFunction}
		\label{cost-skype-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{bigFlows-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/bigFlows_costFunction}
		\label{cost-bigFlows-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{lan-diurnal-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/Lan_costFunction}
		\label{cost-lan-pcap}
	}
	\hspace{0mm}
	\subfloat[\textit{wan-pcap}]{
		\includegraphics[width=75mm]{figures/ch4/Wan_costFunction}
		\label{cost-wan-pcap}
	}
	\caption{Cost function for each one of the datasets used in this validation process}
	\label{fig:cost-function}
\end{figure}

\begin{algorithm}[ht!]
	\caption{stochasticModelFitting}
	\label{alg:stochasticModelFitting}
	\begin{algorithmic}[1]
		\small		\Function{stochasticModelFitting}{$interArrivalData, criterion$}
		\State $m = interArrivalData.size$
		\State $interArrivalData = interArrivalData + MIN\_TIME$
		\If{$m < MINIMUM\_AMOUNT\_OF\_PACKETS$}
		\State $model\_list = \{constant\}$
		\Else
		\State $model\_list = \{weibull, pareto\_lr, pareto\_mlh, exponential\_me, exponential\_lr, normal,$
		\State $cauchy, constant\}$
		\EndIf

		\For{$model$ \textbf{in} $model\_list$}
		\State $model.fitting\_model(interArrivalData)$
		\EndFor
		\State $model\_list.sort(criterion)$
		\State \textbf{return} $model\_list$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

Also, except by the Pareto function modeled using the Maximum likelihood method, have comparative results between the simulations and the AIC/BIC goes. The best fittings according to the AIC/BIC usually returned very accurate models, with a small error between the mean and fractal level, and correlation close to one. The models selected as the worsts usually returned poor results.

Also, it is important to notice that in some cases, some stochastic functions may perform poorly, and in other provide an accurate fitting, what justify the application of the criteria in all new experiments. For example, Weibull usually performs pretty well, but in some cases, perform poorly, and in others may even diverge.

We do not rely on only one type of parameterization. This turns our methodology more robust, since a linear regression may diverge. But always there will be a peaceable model, since our estimations for Normal, Exponential (Me) and Pareto (MLH) cannot. Models which the linear regression diverges, will have very high and positive BIC/AIC estimations, and will not stand as primary options.
